\documentclass{fast-nuces-bs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{blindtext}
\usepackage{mathptmx}% Times Roman font
\usepackage[T1]{fontenc}
\usepackage{lipsum} 
\usepackage{sectsty}
\usepackage{hyperref}
\usepackage{tikz-uml}
\usepackage{titlesec}

\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}

% Redefine \cleardoublepage to \clearpage to avoid blank pages
\let\cleardoublepage\clearpage

% Information about the Thesis 
% -----------------------------------------------------------------------------
% (All are compulsory, do not delete any line other than author Information)
% For e.g., usually there are 3 students in a group, so leave authorone, 
% authortwo, and authorthree, and delete authorfour.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\department{Department of Computer Science}
\faculty{Computer Science}
\degreeyear{2024}
\degreemonth{June}
\degreename{Bachelors in Computer Science}
\campuscity{Peshawar}
\authorone{Dawood Sarfraz}{20P-0153}
\authortwo{Waleed Akram}{20P-0640}
\authorthree{Shoaib Akhtar}{20P-0147}
\supervisor{Dr. Muhammad Amin}
\sessionduration{2020-2024}
\deanname{Dr. Dean Computing}
\directorname{Dr. Omar Usman Khan}
\hodname{Mr. Fazl-e-Basit}
\fypcoordinatorname{Mr. Haroon Zafar}
\title{MetaMed VR: Enhancing Medical Education through Immersive Virtual Reality}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Former document starts below this
\begin{document}
	
	\begin{acknowledgements}
		This project would not have been possible without the support of many dedicated individuals. Our deepest gratitude goes to our advisor, Dr. Muhammad Amin, for his invaluable feedback and unwavering guidance throughout the numerous revisions. We are also profoundly thankful to our coordinator, Mr. Haroon Zafar, for his continuous support and encouragement.
		
		We extend our sincere thanks to the entire Computer Science faculty for their mentorship and valuable time. Additionally, we are grateful to the National University of Computer and Emerging Sciences for providing the opportunity and financial support necessary to bring this project to fruition.
	\end{acknowledgements}
	
	\begin{abstract}
		The rapid evolution of technology continues to redefine traditional educational paradigms. This report delves into the pioneering exploration of leveraging Immersive Virtual Reality (VR) to transform medical education. Focused on the project \textbf{" Enhancing Medical Education through Immersive Virtual Reality (MetaMed) "} our study aims to revolutionize the pedagogical landscape of medical training.
		\\
		In the initial phase of our project, we embarked on a journey to harness cutting-edge VR technology. The objective was to create immersive learning environments that simulate real-world medical scenarios, allowing students to engage in interactive, hands-on learning experiences. Through the integration of advanced VR techniques, our project aspires to bridge the gap between theoretical knowledge and practical application, fostering a deeper understanding of medical concepts.
	\end{abstract}
	
	\include{sections/chapter1}
	\include{sections/chapter2}
	\include{sections/chapter3}
	\include{sections/chapter4}
	\include{sections/chapter5}
	\include{sections/chapter6}
	\include{sections/chapter7}
	\include{sections/chapter8}
	\include{sections/chapter9}
	\include{sections/chapter10} 
	\include{sections/chapter11}
	\include{sections/conclusions}
	
	%\appendix
	%\include{appendix1/appendix1}
	
	\bibliographystyle{plain}
	\bibliography{bib} 
	\addcontentsline{toc}{chapter}{References} 
	
\end{document}
